A Symbolic Decision Procedure for GKAT

### 2024-05-14 notes.tex
typo

    (* all of the following condition needs to be true for all atoms *)
    forall ([*\(α ∈ \At\)*]): 
        match [*\(δ(s, α), δ(t, α)\)*] with 
            [*\(\accept, \accept\)*] -> true 
            [*\((s', p), (t', q)\)*] -> 
                if p = q 
                    then equiv s' t' 
                    else is_dead s' && is_dead t'
            [*\((s', p), \reject\)*] -> is_dead s'
            [*\(\reject, (t', p)\)*] -> is_dead t'
            [*\(\reject, \reject\)*] -> true 
            _ -> false
\end{lstlisting}
TODO: I think I still need to use one of those algorithm package...

>>>>

    (* all of the following condition needs to be true for all atoms *)
    forall ([*\(α ∈ \At\)*]): 
        match [*\(δ(s, α), δ(t, α)\)*] with 
            [*\(\accept, \accept\)*] -> true 
            [*\((s', p), (t', q)\)*] -> 
                if p = q 
                    (* mark s and t as bisimular and check the rest*)
                    then union s t; equiv s' t' 
                    else is_dead s' && is_dead t'
            [*\((s', p), \reject\)*] -> is_dead s'
            [*\(\reject, (t', p)\)*] -> is_dead t'
            [*\(\reject, \reject\)*] -> true 
            _ -> false
\end{lstlisting}
TODO: I think I still need to use one of those algorithm package...
